Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\bf Problem $\bm{\mathscr{D}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles. In the {\em find-lowest} version of the problem, the goal is to report, for each rectangle $r \in R$, the lowest segment in $\cross_H(r)$ (see its definition in \eqref{eqn:cross}). If no segment in $H$ crosses $r$, output nothing for $r$.  Figure~\ref{fig:probs}d gives an example where $H = \set{h_1, h_2, h_3}$ and $R = \set{r_1, r_2}$; the output is $\set{(r_1, h_3), (r_2, h_2)}$. The problem can be solved in $O(n \log n)$ time where $n = |H| + |R|$, as shown in Appendix~\ref{app:bricks}.

>>>>

\extraspacing {\bf Problem $\bm{\mathscr{D}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles. In the {\em find-lowest} version of the problem, the goal is to report, for each rectangle $r \in R$, the lowest segment in $\cross_H(r)$; see \eqref{eqn:cross} for the definition of $\cross_H(r)$. If no segment in $H$ crosses $r$, output nothing for $r$.  Figure~\ref{fig:probs}d gives an example where $H = \set{h_1, h_2, h_3}$ and $R = \set{r_1, r_2}$; the output is $\set{(r_1, h_3), (r_2, h_2)}$. The problem can be solved in $O(n \log n)$ time where $n = |H| + |R|$, as shown in Appendix~\ref{app:bricks}.
